---
title             : "Unity in diversity: Children from 17 communities process gaze in similar ways"
shorttitle        : "Title"

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"
    role:
      - "Writing - Review & Editing"
      - "Supervision"

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  Representing 46% of the world's population
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : "r-references.bib"
csl: science.csl

floatsintext      : yes
linenumbers       : yes
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

Social cognition is a defining aspect of the human species []. It is supposed to enable unique forms of communication and cooperation that underlie cumulative cultural evolution and the formation of complex societies []. The eyes are the proverbial window to the mind and the starting point for a majority of social reasoning processes. Gaze is used to infer the focus of attention which is a critical aspect of coordinated activities including communication and cooperation []. Developmentally, gaze following emerges early in infancy; before the onset of intentional communication or any form of cooperation []. Furthermore, individual differences in gaze following predict later life outcomes [], for example, gaze following in the context of episodes of joint attention predicts later communicative abilities []. Underlying this narrative is the wide-held assumption that gaze following works and develops in the same way across human societies. This claim, however, lacks a solid empirical foundation. 

We conducted a large-scale study on the development of gaze following abilities. The XXXX participants (age ) in the study lived in 17 different communities spread over five continents. The countries from which data was contributed to the study represented 46% of the world's population. Communities covered a broad spectrum of geographical locations, social and political systems, languages and subsistence styles [Fig. 1]. While previous comparative work focused on the onset of gaze following in infancy [], our goal was to study potentially universal developmental and processing signatures that would support the interpretation that gaze following is building block of social cognition in human societies all over the world; or not. 

For this purpose, we used an animated picture book tablet task in which participants were asked to locate a hidden object based on observing an agents gaze. Children watched a balloon disappear behind a hedge. An agent followed the trajectory of the balloon with their eyes. The key dependent variable, was the precision with which children located the agent's focus of attention, that is, the deviation between where the agent looked (where the object was) and where the child thought the agent looked. Visuals and voice recordings in the task were adapted specifically to each of the 17 communities (Fig. 1). In previous work, this task showed excellent individual-level measurement properties []. Thus, in addition to group-level trends, we were able to investigate individual-level variation. 

As the first step, we investigated developmental gains. Across all 17 communities, we found a substantial increase in average levels of precision with age (range: $\beta_{min}$ = , 95% HDI () to $\beta_{max}$ = ()). There were marked differences between communities: urban communities around the globe showed higher levels of precision compared to rural communities. We return to this result below. However, differences between communities were small compared to differences between individuals: communities did not form homogeneous clusters but largely overlapping distributions in that some individuals from communities with a lower average level of precision (e.g. ) performed better compared to some individuals from a setting with a very high average level of precision. Furthermore, in all communities some 4-year-olds outperformed children two years older than them.

Consistent developmental gains to not inform us about the cognitive processes children use when location the agent's focus of attention. Recent computational work modeled gaze following as social vector estimation []. When observing the eyes, onlookers estimate a vector from the center of the eye through the pupil. The focus of attention is the location wherever the estimated vector hits a surface (Fig. XX). The estimation process is not perfect, but each individual has a systematic level of uncertainty, which is conceptualized as the cause of individual differences. Importantly, this process model predicts a clear performance signature in our cross-cultural gaze following task. Trials in which the agent looks further away from the center (i.e. to the left or right side of the screen) should be more difficult, that is, result in lower levels of precision, compared to trials in which the agent looks closer to the middle. This prediction is best understood by considering a similar phenomenon: pointing a torch light to a flat surface. The width of the light beam represents each individual's level of uncertainty in vector estimation. When the torch is directed straight down, the light beam is concentrated in a relatively small area. When the torch is rotated to the side, the the light from one half of the cone must travel further than the light from the other half to reach the surface. As a consequence, the light is spread over a wider area. 

The processing signature was clearly visible across all 17 communities. Precision decreased when the agent looked at locations further away from the center (fixed effect: $\beta$ = (), community-level effects: Fig. 2). Visualization of the data showed the predicted u-shaped pattern in all communities. These results speak for comparable cognitive processes being used by children in all communities. There is, however, an alternative way in which the u-shaped pattern might arise: it would also arise when participants ignore the agent's gaze and instead always selected the middle of the screen (center bias). To rule out this alternative explanation, we directly compared three cognitive models that made different assumptions about how participants' responses were generated: the focal vector-based gaze estimation model described above, a center-bias model where participants always select the center and a random guessing model where participants select random locations. For every community, we found overwhelming support for the gaze estimation model (min $BF_{10}$ < 1000 for comparisons with both alternative models). Taken together, children from the 17 communities we tested likely processed gaze in similar ways.

What is left to explain are the marked community- and individual-level differences. In addition to the gaze-following task, caregivers filled out a small questionnaire about children's access to screen-based technology and the composition of their household. On an individual level, we found that across communities, children with access to touchscreen devices had higher levels of precision (fixed effect: $\beta$ = (), community-level effects: Fig. 2). On a community level, we also saw that average performance was lowest in the communities in which touchscreen devices were the least frequent (Fig. 3). Thus, methodological factors likely explained the marked differences between communities. 

On an individual level, other factors likely generated individual differences because there was substantial variation even in communities in which almost all children had access to touchscreens. Previous work suggested that social cognition develops in social interaction [], in particular, with older siblings. We found tentative support for this idea in the form of a small but consistent effect in the direction that participants living together with more children older than themselves had slightly higher levels of precision (fixed effect: $\beta$ = (), community-level effects: Fig. 2).

Following and understanding gaze is a foundational building block of human social cognition []. A substantial body of work has explored the developmental onset of gaze following in a few selected cultural settings []. The data reported here provides evidence that children all over the world process gaze in the same way. Key performance signatures of a model that sees gaze following as a form of social vector estimation were found in the data of all 17 distinct cultural communities. The cognitive processes underlying gaze following are thus likely to be rooted in humans' evolved cognitive architecture, which is later refined during social interaction. The evolutionary roots of these processes might possibly lie much deeper as primates from a wide range of species follow gaze []. Yet, if they also show the same processing signatures has yet to be explored.      

There are important limitations to this study. The methodological factors that influenced performance might have overshadowed individual and community-level differences that originate from other sources. Importantly, this does not affect our interpretation of the data as evidence for shared cognitive processing because the key processing signatures were present in all communities. The role that social interaction plays as a potentials driver of development and source of individual differences is vastly under-explored in the current study. The small effect of the exposure to older children does not indicate which aspects of social interaction enhance gaze processing. Naturalistic data recording social interactions across communities would offer crucial information to close this explanatory gap. 

The evidence presented here holds far-reaching implications. Our work pioneers a methodological approach that introduces solid individual-level measurement to the cross cultural study of cognitive development. As such, it serves as a blueprint for future research on a broad spectrum of cognitive abilities. Most importantly, this study offers a much-needed empirical foundation for theories on human nature. The finding that children from diverse cultures deploy similar cognitive processes in interpreting gaze points to an evolutionary basis of basic social cognition which is refined during development, presumably through social interaction. 




# Results

# Discussion 



# Methods

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


\newpage

# References

::: {#refs custom-style="Bibliography"}
:::
